What is MaxEnt?

### 2015-06-14 ms.tex
Some references

%To keep things concrete, suppose all of the unknown parameters are positive,
%and our prior is an improper uniform distribution:

%\begin{eqnarray}
%q(\boldsymbol{x}) \propto
%\left\{
%\begin{array}{lr}
%1, & \forall x_i > 0\\
%0, & \textnormal{otherwise}.
%\end{array}
%\right.
%\end{eqnarray}

\begin{thebibliography}{}
Jaynes, E. T., 1979, `Where do we Stand on Maximum Entropy?' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
\end{thebibliography}

>>>>

\begin{thebibliography}{}
\bibitem[Caticha(2008)]{2008arXiv0808.0012C} Caticha, A.\ 2008.\ Lectures 
on Probability, Entropy, and Statistical Physics.\ ArXiv e-prints 
arXiv:0808.0012.

\bibitem[Caticha and Giffin(2006)]{2006AIPC..872...31C} Caticha, A., 
Giffin, A.\ 2006.\ Updating Probabilities.\ Bayesian Inference and Maximum 
Entropy Methods In Science and Engineering 872, 31-42.

\bibitem[Giffin and Caticha(2007)]{2007AIPC..954...74G} Giffin, A., 
Caticha, A.\ 2007.\ Updating Probabilities with Data and Moments.\ Bayesian 
Inference and Maximum Entropy Methods in Science and Engineering 954, 
74-84.

\bibitem[Jaynes(1979)]{stand_on_entropy} Jaynes, E. T., 1979, ``Where do we Stand on Maximum Entropy?'' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
\end{thebibliography}
